Package Interconnection

### 2021-09-26 analysis/doe-pkgs-analysis.Rmd
Modify sankey and network diagram.

# pivot longer the data frame by its type 
pkg_tidy_long_type <- pkg_tidy %>%
  unnest(type) %>%
  unnest(date) %>%
  unnest(domain) %>%
  mutate(year = year(ymd(date))) 
```

```{r}
# summarise the packages based on its type
pkg_tidy_long_type %>%
  filter(relevance != "no") %>%
  group_by(type) %>%
  count() %>%
  arrange(desc(n))
```

@@

```{r}
sankey_data <- pkg_tidy_long_type %>%
  select(year, domain, type) %>%
  group_by(domain, type) %>%
  count() %>%
  ungroup()

@@

type <- sankey_data %>%
  distinct(node = type)

>>>>

# pivot longer the data frame by its type 
pkg_tidy_long_type <- pkg_tidy %>%
  unnest(type) %>%
  unnest(date) %>%
  unnest(domain) %>%
  unnest(type2) %>%
  mutate(year = year(ymd(date)))

pkg_type <- pkg_tidy %>%
  unnest(type2) %>%
  unnest(domain)
```

```{r}
# summarise the packages based on its type
pkg_type %>%
  group_by(type2) %>%
  count() %>%
  arrange(desc(n))
```

@@

```{r}
sankey_data <- pkg_type %>%
  select(domain, type2) %>%
  group_by(domain, type2) %>%
  count() %>%
  ungroup()

@@

type <- sankey_data %>%
  distinct(node = type2)

### 2021-09-26 paper/package_interconnection.Rmd
Modify sankey and network diagram.

# create the graph
ggraph(routes_tidy, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm')) + 
  geom_node_point(aes(color = note), size = 4) + 
  geom_node_text(aes(label = name_add), repel = TRUE, size = 3.1) +
  #scale_color_manual(values = c("blue", "tomato", "magenta", "grey50", "#48C9B0", "#C0392B", "#F1C40F")) +
  theme_graph() 
```

@@

ggraph(routes_tidy_facet, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = note), size = 4) +
  geom_node_text(aes(label = name_add), repel = TRUE, size = 3.5) +
  theme_graph() +
  facet_nodes(~note) +
  #scale_color_manual(values = c("blue", "tomato", "magenta", "#48C9B0", "#C0392B", "#F1C40F"), 
                    # guide = "none") +
  th_foreground(foreground = "grey80",  border = TRUE) +
  theme(legend.position = "none")
```

>>>>

# create the graph
ggraph(routes_tidy, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm')) + 
  geom_node_point(aes(color = note), size = 4) + 
  geom_node_text(aes(label = name_add), repel = TRUE, size = 3.1) +
  scale_color_manual(values = c("blue", "tomato", "magenta", "#48C9B0", "#C0392B", "#F1C40F", "grey50", "green")) +
  theme_graph() 
```

@@

ggraph(routes_tidy_facet, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = note), size = 4) +
  geom_node_text(aes(label = name_add), repel = TRUE, size = 3.5) +
  theme_graph() +
  facet_nodes(~note) +
  scale_color_manual(values = c("blue", "tomato", "magenta", "#48C9B0", 
                                  "#C0392B", "#F1C40F", "green"), 
                     guide = "none") +
  th_foreground(foreground = "grey80",  border = TRUE) 
```
